Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers

### 2018-10-10 reports/preprint.tex

When comparing Tables \ref{tab:water} and \ref{tab:liptab} it is clear that the volume of the lipid tails are significantly lower in the current measurements than found previously, by other techniques.
It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails.
Such a reduction has been shown previously\cite{Campbell2018}, where it was rationalised by the compaction of the monolayer at elevated surface pressure.
In that work, the optimal value of the tail volume for DPPC was found to be \SI{772}{\cubic\angstrom} at a surface pressure of \SI{35}{\milli\newton\per\meter}, this agrees well with the value of \input{../output/dppc/vt.txt}\si{\cubic\angstrom} found in this work at surface pressures of 15, 20, 25, and \SI{30}{\milli\newton\per\meter}.
The reduction was found to be \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, this is in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small \emph{et al.}\cite{Small1984}.
DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
However, our value is similar to that found for DMPC on DES, which has the same tail structure and suggests that our results are at least self-consistent.

>>>>

When comparing Tables \ref{tab:water} and \ref{tab:liptab} it is clear that the volume of the lipid tails are significantly lower in the current measurements than found previously, by other techniques.
It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails.
Such a reduction has been shown previously\cite{Campbell2018}, where it was rationalised by the compaction of the monolayer at elevated surface pressure.
In that work, the optimal value of the tail volume for DPPC was found to be \SI{772}{\cubic\angstrom} at a surface pressure of \SI{35}{\milli\newton\per\meter}, this agrees well with the value of \input{../output/dppc/vt.txt}\si{\cubic\angstrom} found in this work at surface pressures of 15, 20, 25, and \SI{30}{\milli\newton\per\meter}.
The reduction was found to be \SIrange{8}{12}{\percent} for DPPC, DMPC and DLPC when compared with literature sources at \SIrange{24}{30}{\celsius}, this is in good agreement with the maximum compression percentage of \SI{15}{\percent} noted by Small \emph{et al.}\cite{Small1984}.
DMPG shows a small increase in the tail volume relative to the literature value quoted at lower temperature.
However, this value is similar to that found for DMPC on DES, which has the same tail structure and suggests that our results are at least self-consistent.
